The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-24 manuscript/manuscript.Rnw
include too many alignment in star plot
we're not indicating the place/time of collection

Fetal tissue was collected from the placenta of eight mammalian
species (\human [human], \bonobo [bonobo], \dog [domestic dog], \cow
[domestic cow], \elephant [African savanna elephant], \opossum [gray
short-tailed opossum], \galili [blind mole rat from Upper Galilee],
\carmeli [blind mole rat from northern Israel]
\cite{Nevo2001:adaptiveradiationofblindsubterraneanmole}). Information
on specimen ID, place and time of collection, and collector is shown
for each sample in Supplemental \cref{tab:srr_numbers}. In the case of
\bonobo, \cow, and \elephant, the placenta was collected at term upon
expulsion from the mother following delivery. Placental tissue from
\human was collected upon delivery via a cesarean section. Near-term
placental tissue from \dog was collected upon the death of the mother
from a car accident. Placental tissue from \opossum was sampled at
fetal stage 32, roughly one day prior to birth. Only the fetal portion
of the placenta was sampled at the maternal-fetal interface (i.e.
villous portion for \human, \bonobo, \dog, and \elephant; cotyledon
for \cow; diffuse placenta for \opossum). All tissues were collected
and stored in RNAlater (Life Technologies, Carlsbad, CA) until RNA
isolation could be performed. Tissues were homogenized in Trizol, and
total RNA was isolated following the manufacturer's instructions. RNA
was further purified using RNeasy Midi Kit (Qiagen, Valencia, CA), in
conjunction with the RNase-Free DNase Set (Qiagen, Valencia, CA),
following the manufacturer’s protocol to remove any contaminating DNA
from the sample. Total RNA was then evaluated on a Nanodrop 1000
(Thermo Scientific, Wilmington, DE) and an Agilent Bioanalyzer 2100
(Santa Clara, CA) to confirm concentration and quality of the
isolation. RNA quality was assessed using A260/A280 and A260/A230
absorbance values.

@@

\subsection{Annexin Complex}

\subsection{Human Specific Expression Shifts and the Evolution of Pre-eclampsia}

>>>>

Fetal tissue was collected from the placenta of eight mammalian
species (\human [human], \bonobo [bonobo], \dog [domestic dog], \cow
[domestic cow], \elephant [African savanna elephant], \opossum [gray
short-tailed opossum], \galili [blind mole rat from Upper Galilee],
\carmeli [blind mole rat from northern Israel]
\cite{Nevo2001:adaptiveradiationofblindsubterraneanmole}). Information
on specimen ID, and collector is shown for each sample in Supplemental
\cref{tab:srr_numbers}. In the case of \bonobo, \cow, and \elephant,
the placenta was collected at term upon expulsion from the mother
following delivery. Placental tissue from \human was collected upon
delivery via a cesarean section. Near-term placental tissue from \dog
was collected upon the death of the mother from a car accident.
Placental tissue from \opossum was sampled at fetal stage 32, roughly
one day prior to birth. Only the fetal portion of the placenta was
sampled at the maternal-fetal interface (i.e. villous portion for
\human, \bonobo, \dog, and \elephant; cotyledon for \cow; diffuse
placenta for \opossum). All tissues were collected and stored in
RNAlater (Life Technologies, Carlsbad, CA) until RNA isolation could
be performed. Tissues were homogenized in Trizol, and total RNA was
isolated following the manufacturer's instructions. RNA was further
purified using RNeasy Midi Kit (Qiagen, Valencia, CA), in conjunction
with the RNase-Free DNase Set (Qiagen, Valencia, CA), following the
manufacturer’s protocol to remove any contaminating DNA from the
sample. Total RNA was then evaluated on a Nanodrop 1000 (Thermo
Scientific, Wilmington, DE) and an Agilent Bioanalyzer 2100 (Santa
Clara, CA) to confirm concentration and quality of the isolation. RNA
quality was assessed using A260/A280 and A260/A230 absorbance values.

@@

\subsection{Annexin and Fetal Immunotolerance}

\DLA{Finish out this section siting Aarli work and Linke work}

\subsection{\human Specific Expression Shifts and the Evolution of Pre-eclampsia}
